Visualizations for the manuscript

### 2022-05-11 metanalysis_visualization/manuscript_Figures.Rmd
code added to plot sex ITS in the same way than the rest of ITS plots

>>>>

### Alternative plot

```{r annotation boostrap disorders}
names_sex <- unique(df_coefficients_boot_sex$sex)

plot_annotations_sex <- df_coefficients_boot_sex %>% 
  group_by(sex) %>% 
  group_map( bootstrap_pvalue_calculation ) %>%
  set_names(names_sex) %>% 
  lapply(FUN = function(vec) {
    paste0("Coeffs differences: ",
           vec$observed_diff,
           " (pvalue: ",
           format.pval(vec$pvalue, 
                       eps = 10**-5),
           ")")
  }) %>% 
  unlist()
plot_annotations_sex_df <- data.frame(
  sex = names(plot_annotations_sex), 
  label = plot_annotations_sex
)
```

```{r}
bootstrapped_fitted_sex %>% 
  mutate(period = recode_factor(period, "before_pandemic" = "Before pandemic onset", "during_pandemic" = "Since pandemic onset")) %>% 
  ggplot(aes(x = time_p, y = predicted, group = interaction(iteration, period))) +
  facet_wrap("sex",
             scales = "free_y",
             labeller = label_wrap_gen(width = 35,multi_line = TRUE)) +
  geom_line(aes(color = period),
            alpha = 0.03) +
  geom_line(data = quantile_bootstrapped_fitted_sex,
            aes(y = value, group = interaction(quantiles, period)),
            linetype = "dashed") +
  geom_line(data = quantile_bootstrapped_fitted_sex[quantile_bootstrapped_fitted_sex$quantiles == "50%", ],
            aes(y = value, group = period)) +
  geom_point(data = patients_hospitalized_agg_sex_total,
             aes(y = percentage, group=NULL),
             alpha = 0.5) +
  scale_colour_manual(values = cbPalette) +
  scale_x_date(breaks = "1 month", labels=date_format("%b-%y"), expand=c(0.03,0))+
  guides(color = guide_legend(override.aes = list(alpha = 1))) +
  geom_label(data = plot_annotations_sex_df, 
             aes(label=label), 
            x = -Inf,
            y = +Inf,
            hjust = 0,
            vjust = 1,
            size = 4,
            inherit.aes = FALSE) +
  labs(x = "Calendar dates",
       y = "Percentage",
       color = "Period") +
  theme(strip.text = element_text(size = 10),
        axis.text.x=element_text(angle = 45, hjust=1, size = 8),
        axis.text.y = element_text(size = 8), 
        axis.title.x = element_text(size = 8),
        axis.title.y = element_text(size = 8),
        title = element_text(size = 14),
        plot.subtitle = element_text(size = 8, face = "italic"), 
        legend.position = "bottom") 
ggsave("figure4_boostrapped_sex.png", height = 15, width = 25, units = "cm")
```

#### Oiriginal plot
